Analysis of COVID-19 Cases in Toronto During 2020: Trends by Age, Gender, and Sources of Infection

### 2024-09-27 paper/paper.qmd
Final version of the paper

The paper structured as follows: Firstly, @sec-data-overview provides a description of the dataset. This includes introduction of data source and data cleaning process (@sec-data-source), and explanations of variables and measurement (@sec-variable). Then, @sec-visual displays all visualizations of the data, including distribution by age groups (@sec-age), distribution by gender (@sec-gender), and distribution by sources of infection (@sec-source-infection). Then, @sec-result presents the results of data analysis. @sec-outbreak discusses how counts of COVID-19 cases were associated with outbreaks; @sec-age-same-source compares the counts of COVID-19 cases of different age groups within the same source of infection; and @sec-source-same-age compares the counts of cases of different sources of infection within the same age group. Finally, @sec-appx includes supplementary information on data cleaning process (@sec-appx-cleaning) and summarized statistics of each variable (@sec-appx-stats). References of the paper are listed at the end.

@@

## Visualization {#sec-visual}

>>>>

The paper structured as follows: Firstly, @sec-data-overview provides a description of the dataset. This includes introduction of data source and data cleaning process (@sec-data-source), and explanations of variables and measurement (@sec-variable). Then, @sec-analysis displays all visualizations of the data, including distribution by age groups (@sec-age), distribution by gender (@sec-gender), and distribution by sources of infection (@sec-source-infection). Then, @sec-result presents the results of data analysis. @sec-outbreak discusses how counts of COVID-19 cases were associated with outbreaks; @sec-age-same-source compares the counts of COVID-19 cases of different age groups within the same source of infection; and @sec-source-same-age compares the counts of cases of different sources of infection within the same age group. Finally, @sec-appx includes supplementary information on data cleaning process (@sec-appx-cleaning) and summarized statistics of each variable (@sec-appx-stats). References of the paper are listed at the end.

@@

## Analysis {#sec-analysis}
